Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-09 main.tex
Slight simplication

% Notational conventions
\newcommand{\HIGH}{\textsc{h}}
\newcommand{\LOW}{\textsc{l}}
\newcommand{\word}{W}
\newcommand{\addr}{A}
\newcommand{\WORDS}{{\mathcal W}}
\newcommand{\reg}{R}
\newcommand{\REGS}{{\mathcal R}}
\newcommand{\mach}{M}
\newcommand{\MACHS}{{\mathcal M}}
\newcommand{\PC}[1]{\PCname(#1)}
\newcommand{\PCname}{\textsc{pc}}
\newcommand{\polname}{P}
\newcommand{\pol}[1]{\polname(#1)}
% \newcommand{\trace}[1]{\overline{#1}}
\newcommand{\contour}{C}
\newcommand{\CONTOURS}{{\mathcal C}}
\newcommand{\stepsto}{\Longrightarrow}
\newcommand{\stepstounder}[1]{\stackrel{\mbox{\tiny{$#1$}}}{\Longrightarrow}}
\newcommand{\stepstounderfull}{\stepstounder{\textsc{full}}}
\newcommand{\manystepsto}{\stepsto^\star}

@@

Conventions:
%
\begin{itemize}
\item Words / addresses: $\word,\addr \in \WORDS$
\item Registers: $\reg \in \REGS$
\item Machine states: \bcp{Simplify: define {\em machine components} and
  then a machine state is a function from these to words.}
$\mach \in \MACHS = (\WORDS\rightarrow\WORDS,\, \REGS\rightarrow\WORDS,\,
\WORDS)$
\item Abbreviations:
\\ $\mach(\addr) = \mach.1(\addr)$
\\ $\mach(\reg) = \mach.2(\reg)$
\\ $\mach(\textsc{pc}) = \mach.3$
\end{itemize}

@@

A {\em contour}
$\contour \in \CONTOURS = (\WORDS \cup \REGS \cup \{\PCname\}) \rightarrow \{\HIGH,\LOW\}$ is a
map from machine components to ``security levels,'' where $\HIGH$ marks
locations containing secret or low-integrity data and $\LOW$ marks those
with public or high-integrity data.

>>>>

% Notational conventions
\newcommand{\HIGH}{\textsc{h}}
\newcommand{\LOW}{\textsc{l}}
\newcommand{\word}{W}
\newcommand{\addr}{A}
\newcommand{\WORDS}{{\mathcal W}}
\newcommand{\reg}{R}
\newcommand{\REGS}{{\mathcal R}}
\newcommand{\mach}{M}
\newcommand{\MACHS}{{\mathcal M}}
\newcommand{\PC}[1]{\PCname(#1)}
\newcommand{\PCname}{\textsc{pc}}
\newcommand{\polname}{P}
\newcommand{\pol}[1]{\polname(#1)}
% \newcommand{\trace}[1]{\overline{#1}}
\newcommand{\contour}{C}
\newcommand{\CONTOURS}{{\mathcal C}}
\newcommand{\component}{K}
\newcommand{\COMPONENTS}{{\mathcal K}}
\newcommand{\stepsto}{\Longrightarrow}
\newcommand{\stepstounder}[1]{\stackrel{\mbox{\tiny{$#1$}}}{\Longrightarrow}}
\newcommand{\stepstounderfull}{\stepstounder{\textsc{full}}}
\newcommand{\manystepsto}{\stepsto^\star}

@@

Conventions:
%
\begin{itemize}
\item Words / addresses: $\word,\addr \in \WORDS$
\item Registers: $\reg \in \REGS$
\item Machine components: $\component \in \WORDS \cup \REGS \cup \{
\textsc{pc} \}$
\item Machine states: $\mach \in \MACHS = \COMPONENTS\rightarrow\WORDS$
\end{itemize}

@@

A {\em contour}
$\contour \in \CONTOURS = \COMPONENTS \rightarrow \{\HIGH,\LOW\}$ is a
map from machine components to ``security levels,'' where $\HIGH$ marks
locations containing secret or low-integrity data and $\LOW$ marks those
with public or high-integrity data.
